---
title: "Tyler Pardun - Lab Functions"
author: "Tyler Pardun"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tyler Pardun - Lab Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{rmarkdown::render}

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753pard0003)
```

# Introduction

In this package, 5 functions are defined from previous labs and examples are shown below. 


# Mymult Function
```{r}
MATH4753pard0003::mymult(iter=100,n=10, p=c(1,1,1,1)/4)
```
This function inputs a vector of an arbitrary number of categories with a specified number of iterations and a size n. This function will graph the relative frequencies of n random samples and creates a histogram out of it.

# Myncurve Function
```{r}
MATH4753pard0003::myncurve(a=10, mu=3, sigma=1)
```
This function will input an arbitrary number with a specified mean and standard deviation. The output will be a normal distribution with the probability of x is less than or equal to that specifed number.

# Myplot Function
```{r}
MATH4753pard0003::myquadratic(x=100)
```
This function take an input X value and will return the yhat value from the equation specified in Lab 4.

# Mycltp Function
```{r}
MATH4753pard0003::mycltp(n=20,iter=10000,lambda=10)
```
This function takes a sample size of n, an abirtrary number of iterations and a specifed lambda value for a Poisson distribution. The output consits of a histogram of the density of the discrete values, a barplot of the sampled y values and a probability function of all possible y values.

# Myboot2 Function
```{r}
set.seed(68)
sam=rnorm(20,mean=10,sd=4)
MATH4753pard0003::myboot2(iter=10000,x=sam,fun="mean",alpha=0.05)
```
This function takes a specified distriubtion and will perform a bootstrap sample to it to obtain the lower and upper bounds of a specified confidence interval.

# Myci Function
```{r}
MATH4753pard0003::myci(x=rnorm(30,mean=10,sd=3))
```
This function takes a specified distriubtion and will compute the lower and upper bounds of a the 95% confidence interval.

# Mymlnorm Function
```{r}
y=c(10,12,13,15,12,11,10)
MATH4753pard0003::mymlnorm(y,color='black')
```
This function produces a 3 panel plot for the poisson distribution.

# mybootpval Function
```{r}
set.seed(55);x1=rnorm(30,mean=25, sd=5)
MATH4753pard0003::bootpval(x=x1,mu=22,test="two")
```
This function produces a histogram with accepted and rejected regions from a bootstrap resample from a given sample and a given null hypothesis about the mean of the sample.
